---
title: "Assignment 3 - Diamonds Price Estimation"
author: "Ecemnaz Bay"
date: "9/4/2020"
output: 
  html_document:
    toc: true # table of content true
    toc_depth: 3  # upto two depths of headings (specified by #, ## and ###)
    number_sections: true  ## if you want number sections at each table header
    theme: united  # many options for theme, this one is my favorite.
    highlight: tango  # specifies the syntax highlighting style
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#Required Packages
library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)
library(tidyr)
library(kableExtra)
library(corrplot)
library(grid)
library(lattice)
library(ggpubr)
library(scales)
library(wesanderson)
library(RColorBrewer)
library(Metrics)

```


## Diamonds Price Estimation

That assignment aims to find a prediction model for estimating the price of a diamond given its properties. \
`rDiamonds` data set in `rggplot2` package is used for the assignment. 

Training and test data sets are created. 

```{r Diamonds}
set.seed(503)
diamonds_test <- diamonds %>% mutate(diamond_id = row_number()) %>% 
    group_by(cut, color, clarity) %>% sample_frac(0.2) %>% ungroup()

diamonds_train <- anti_join(diamonds %>% mutate(diamond_id = row_number()), 
    diamonds_test, by = "diamond_id")

diamonds_all <- bind_rows(diamonds_train,diamonds_test)
```

Below is a sample from train data set.

```{r}
  head(diamonds_train)%>%
  kbl(caption = "Sample from Training Data") %>%
  kable_minimal(full_width = F)
  
  
```

Below is a sample from test data set.

```{r}
  head(diamonds_test)%>%
  kbl(caption = "Sample from Test Data") %>%
  kable_minimal(full_width = F) 
  
```

### Correlations Plot


In order to have a clear visualization, a function is used to plot the correlations. (Source can be seen in references section.) 

* Converts all non-numeric variables into numeric ones. 
* Drops duplicates and perfect correlations (correlations with itself).
* Set up the data frame sorted by the highest correlation first to see the raw correlations in a table.

Here, the function is changed to include perfect correlations and duplicates. \
Moreover, it is set to show variables only have a specific significance level above a threshold. \
That threshold is set to 0.05 as the initial default.

```{r}
diamonds_AllForCorr <- select(diamonds_all, -diamond_id)

corr_simple <- function(data=diamonds_AllForCorr,sig=0.05){
  #convert data to numeric in order to run correlations
  #convert to factor first to keep the integrity of the data - each value will become a number rather than turn into NA
  df_cor <- data %>% mutate_if(is.character, as.factor)
  df_cor <- df_cor %>% mutate_if(is.factor, as.numeric)
  #run a correlation and drop the insignificant ones
  corr <- cor(df_cor)
    #prepare to drop duplicates and correlations of 1     
    #corr[lower.tri(corr,diag=TRUE)] <- NA 
    #drop perfect correlations
    #corr[corr == 1] <- NA 
  #turn into a 3-column table
  corr <- as.data.frame(as.table(corr))
  #remove the NA values from above 
  corr <- na.omit(corr) 
  #select significant values  
  corr <- subset(corr, abs(Freq) > sig) 
  #sort by highest correlation
  corr <- corr[order(-abs(corr$Freq)),] 
  #print table
  print(corr)
  #turn corr back into matrix in order to plot with corrplot
  mtx_corr <- reshape2::acast(corr, Var1~Var2, value.var="Freq")
  
  #plot correlations visually
  corrplot(mtx_corr, is.corr=FALSE, tl.col="black", na.label=" ")
}
corr_simple()



```



Structure of variables that has correlation with price with a significance level over 0.05 is as follows :

* Price is a continuous response variable 
* x is a continuous explanatory variable
* y is a continuous explanatory variable
* z is a continuous explanatory variable
* Carat is a continuous explanatory variable
* Color is an ordered factor type of explanatory variable with 7 different levels.
* Table is a continuous explanatory variable
* Clarity is an ordered factor type of explanatory variable with 8 different levels.
* Cut is an ordered factor type of explanatory variable with 5 different levels.

```{r}
str(diamonds_all)
```

Upon correlation table, darker blue and bigger circles denotes higher correlation. \
Thus, 4 variables are selected to build the model:

* x
* y
* z
* Carat

In order to understand distribution of the response variable, price, density plots are used. \
In the below figure, density plots of overall data, test and train sets are combined together. \

Response variable seems to follow a continuous probability distribution. 
Price has a sharp lower bound value of zero (always positive) but no sharp upper bound can be defined. \
As seen in density plots, the tail on the right hand side is longer, so a positive skewness is observed. \
Gamma distributions can be used according to these observations.

```{r}
alldata <- ggplot(diamonds_all, aes(x=price))+
  geom_density(color="slategray3", fill="slategray1")+
  theme_minimal()+
  ggtitle("Density Plot of Whole Data")+
  scale_y_continuous(labels = comma)


traindata <- ggplot(diamonds_train, aes(x=price))+
  geom_density(color="darkseagreen3", fill="darkseagreen1")+
  theme_minimal()+
  ggtitle("Density Plot of Taining Set")+
  scale_y_continuous(labels = comma)



testdata <- ggplot(diamonds_test, aes(x=price))+
  geom_density(color="peachpuff2", fill="peachpuff")+
  theme_minimal()+
  ggtitle("Density Plot of Test Set")+
  scale_y_continuous(labels = comma)


ggarrange(alldata, traindata, testdata, ncol = 1, nrow = 3)


```


### Evaluating Models 

A base model is built including all explanatory variables selected via correlation plot. \
Backward regression is applied to find out the best possible model.

```{r, warning=FALSE }
diamonds_train_forGamma <- na.omit(diamonds_train)
diamonds_test_forGamma <- na.omit(diamonds_test)

Model_1 <- glm(price~x+y+z+carat,family = Gamma,
        data=diamonds_train_forGamma,
        start=c(0.5,0.5,0.5,0.5,0.5))

summary(Model_1)
```

The least significant variable, z is eliminated from th emodel. New model shows imrovement according to AIC.

```{r, warning=FALSE}
Model_2 <- glm(price~x+y+carat,family = Gamma,
        data=diamonds_train_forGamma,
        start=c(0.5,0.5,0.5,0.5))

summary(Model_2)

```

The least significant variable, y is eliminated from the model. New model shows imrovement according to AIC. \

In Model_3 all explanatory variables have significant effect on the price with a significance level of 0.05.

```{r, warning=FALSE}
Model_3 <- glm(price~x+carat,family = Gamma,
        data=diamonds_train_forGamma,
        start=c(0.5,0.5,0.5))

summary(Model_3)
```


Different link functions of Gamma are compared according to their AIC values. \
Identity link function is selected with the lowest AIC value. \
AIC of identity, inverse and log link functions are calculated respectively as follows : 

```{r, warning=FALSE}
for(link in c("identity","inverse","log")){ 
  GlmModel = glm(price~x+carat,
                 family = Gamma(link=link),
                 data=diamonds_train_forGamma,
                 start=c(0.5,0.5,0.5))
  print(AIC(GlmModel)) 
  }


```

Here is the summary of final model :

```{r, warning=FALSE}
FinalModel <- glm(price~x+carat,family = Gamma(link="identity"),
                  data=diamonds_train_forGamma,
                  start=c(0.5,0.5,0.5))

summary(FinalModel)
```

### RMSE Calculation

In order to get insight about prediction performance, RMSE is calculated.

```{r, warning=FALSE }

   pred_TrainData = predict(FinalModel) 
   pred_TestData =  predict(FinalModel,new=diamonds_test_forGamma) 
   
   rmse(diamonds_test_forGamma$price, pred_TestData)

```

### Residual Plot

According to residual plot, constant variance and zero mean assumptions seems to hold for the used model.
  
```{r, warning=FALSE }

FinalModel_TestData <- glm(price~x+carat,family = Gamma(link="identity"),
                  data=diamonds_test_forGamma,
                  start=c(0.5,0.5,0.5))

ggplot(FinalModel_TestData) + 
  geom_point(aes(x=.fitted, y=.resid, col=.resid)) +
  theme_minimal() + 
  ggtitle("Residual Plot") +
  labs(x = "Fitted Values",
       y = "Residuals") +
  scale_color_gradient(low="darkslateblue", high="coral3") +
  labs(col = "Residuals")
  

```
  


### References

* https://towardsdatascience.com/how-to-create-a-correlation-matrix-with-too-many-variables-309cc0c0a57
* http://people.stat.sfu.ca/~raltman/stat402/402L26.pdf
* https://www.mygreatlearning.com/blog/gamma-distribution/
* https://wiki.analytica.com/index.php?title=Gamma_distribution
* https://codeburst.io/2-important-statistics-terms-you-need-to-know-in-data-science-skewness-and-kurtosis-388fef94eeaa
* https://stat.ethz.ch/pipermail/r-help/2009-December/416122.html
* https://www.rdocumentation.org/packages/Metrics/versions/0.1.4/topics/rmse
* https://cran.r-project.org/web/packages/Metrics/Metrics.pdf
* https://stackoverflow.com/questions/36731027/how-can-i-plot-the-residuals-of-lm-with-ggplot

