---
title: "Joins Lecture"
author: "Ecemnaz Bay"
date: "8/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Join two tables: dplyr join examples with comic characters and publishers.

## Data Preparation

```{r DataPrep, messages=FALSE}
library(tidyverse) ## dplyr provides the join functions

superheroes <- tibble::tribble(
       ~name, ~alignment,  ~gender,          ~publisher,
   "Magneto",      "bad",   "male",            "Marvel",
     "Storm",     "good", "female",            "Marvel",
  "Mystique",      "bad", "female",            "Marvel",
    "Batman",     "good",   "male",                "DC",
     "Joker",      "bad",   "male",                "DC",
  "Catwoman",      "bad", "female",                "DC",
   "Hellboy",     "good",   "male", "Dark Horse Comics"
  )

publishers <- tibble::tribble(
  ~publisher, ~yr_founded,
        "DC",       1934L,
    "Marvel",       1939L,
     "Image",       1992L
  )
```


```{r print}
print(publishers)
print(superheroes)
```

# Joins

## Left Join

Return all rows from x, and all columns from x and y. If there are multiple matches between x and y, all combination of the matches are returned. This is a mutating join.

```{r LeftJoin}
left_join(superheroes,publishers,by="publisher")
```

## Inner Join

Return all rows from x where there are matching values in y, and all columns from x and y. If there are multiple matches between x and y, all combination of the matches are returned. This is a mutating join.

```{r InnerJoin}
inner_join(superheroes,publishers,by="publisher")
```

## Semi Join

Return all rows from x where there are matching values in y, keeping just columns from x. A semi join differs from an inner join because an inner join will return one row of x for each matching row of y, where a semi join will never duplicate rows of x. This is a filtering join.

```{r SemiJoin}
semi_join(superheroes,publishers,by="publisher")
```

## Full Join

Return all rows and all columns from both x and y. Where there are not matching values, returns NA for the one missing. This is a mutating join.

```{r FullJoin}
full_join(superheroes,publishers,by="publisher")
```

## Anti Join

Return all rows from x where there are not matching values in y, keeping just columns from x. This is a filtering join.

```{r AntiJoin}
anti_join(superheroes,publishers,by="publisher")
```

## Right Join

```{r RightJoin}
right_join(superheroes,publishers,by="publisher")

```

